\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Use \subsection, not \subsubsection here.
\subsubsection within Appendix G was creating labels "G.0.1 E1",
"G.0.2 E2", "G.0.3 E3".

\subsubsection{E1} 
In E1, any connection to Tor worked. Configuring bridges and proxies was optional.  
Observations in E1:

@@

\subsubsection{E2} 
In E2, a bridge was required to connect. Any of the hardcoded bridges from the dropdown menu, as well as any custom bridges acquired out of band would work. Configuring a proxy was optional.
Observations in E2:

@@

\subsubsection{E3}
In E3, a bridge was required to connect. Most of the hardcoded bridges in the dropdown menu do not work, with the exception of meek-amazon, meek-azure, and meek-google. Custom bridges can also work. Configuring a proxy was optional.
Observations in E3:

>>>>

\subsection{E1} 
In E1, any connection to Tor worked. Configuring bridges and proxies was optional.  
Observations in E1:

@@

\subsection{E2} 
In E2, a bridge was required to connect. Any of the hardcoded bridges from the dropdown menu, as well as any custom bridges acquired out of band would work. Configuring a proxy was optional.
Observations in E2:

@@

\subsection{E3}
In E3, a bridge was required to connect. Most of the hardcoded bridges in the dropdown menu do not work, with the exception of meek-amazon, meek-azure, and meek-google. Custom bridges can also work. Configuring a proxy was optional.
Observations in E3:
